\title{Lab report on subject 001}
\author{
        John~O.~Woods,~Ph.D. \\
            \and
        Amie~E.~Hinds,~M.S. \\
            \and
        Luke Shafer,~M.S. \\
        R.~Daneel~Olivaw~Corporation\\
        908 Winston St., Suite \textsc{g} \\
        Houston, Texas 77009
}
\date{\today}

\documentclass[10pt]{article}

\begin{document}
\maketitle

%\begin{abstract}
%This is the paper's abstract \ldots
%\end{abstract}

\section{Description}

Subject consists of two parts, which we refer to as the gem and the setting. The purpose is unknown. Separation of the gem from the setting would likely have damaged the subject, which was contraindicated in the instructions we received and limits the types of tests that can be performed.
% measurements
% precise description of the stone
% precise description of the setting

The gem is transparent yellow, resembling lime citrine, and appears to have been cut precisely.
% rutilated quartz
% blue topaz
The setting is metallic, with a layer of what may be either oxidation or some sort of protective coating; the oxidization or coating has been scraped off on the setting's edges.

\section{Methods and Results}
We endeavored to obtain as much information about the subject as possible with as little potential impact on it as was feasible.
Throughout our analysis, we attempted to limit our methods such that no intervention on our part was more extreme than the natural forces to which the subject was likely subjected prior to discovery.

\subsection{Basic physical characteristics}
While measurement of an object's mass seems so trivial as to belong in a grade-school lab report, our observations of the subject have led us to exercise a great deal of skepticism regarding the standard methods.
For example, a digital laboratory scale expresses its measurement in grams, which is a mass measurement --- but, in fact, the scale provides a measurement of force, not mass, and converts according to a calibration to the local gravitational field.

Several assumptions are implicit in such a measurement:
\begin{enumerate}
\item The object is subject only to gravitational force, and other forces (\textit{e.g.} magnetic) are tiny in comparison.
\item The object contains no regions that are of lower density than the atmosphere. Imagine, for example, a chamber containing helium at atmospheric pressure. Such a chamber would have an apparent weight less than that of an equivalent chamber containing standard atmosphere. Similarly, a chamber containing nothing --- a vacuum --- would weigh less than either the helium chamber or the atmosphere-containing chamber.
\item The object's temperature is at equilibrium with the environment (though this is only significant for gases and not solid objects, we mention it to be exhaustive in the face of confusing experimental results).
\end{enumerate}

Based on our observations, none of these assumptions necessarily applies.
Firstly, the subject produces a stronger than expected magnetic field based upon its apparent composition, and confusingly, the subject's dipole moment appears to rotate.
Not only does the dipole moment rotate, but it does so seemingly \textit{in tandem} with the placement of either a magnetometer or a simple compass relative to the artifact.
Bewilderingly, the magnetic force appears to fall off more quickly as distance increases than would be expected for, say, a current-carrying loop.
We observed that, rather than obeying an inverse-cube law, the magnetic force seems consistent with an inverse-fifth or sixth-power law.

We next attempted to observe the weight of the subject, but found that the weight changed as we re-oriented the subject.
Indeed, when we cycled back through the orientations a second time, the apparent weight differed by up to around five percent from the first set of measurements.
When tested in the early afternoon, the scale recorded an average mass of 40.2 grams with a standard deviation of 1.2 grams.
We repeated the experiment an hour later and recorded an average mass of 41.5 grams --- again with a standard deviation of 1.2 grams.
Unfortunately, we were not allowed to keep the artifact any longer, which rather limited our ability to discern any meaningful trend.

However, one of us (Amie) noticed a peculiarity: the subject behaves extremely oddly when placed in a centrifuge.
We lacked the proper measurement tools, but observed that a 40-gram weight placed on the opposite end of a 0.25-meter centrifuge from the artifact produced a substantial imbalance.
We calculated a difference of roughly a tenth of a newton (order of magnitude, not exact) between the weight (mean) due to gravity and the weight due to centripetal acceleration.
It does not escape our notice that this odd behavior could actually allow the subject to be used as an energy source --- though further study is needed to determine whether the apparent weight correlates with the temperature.

We attempted to ascertain the volume of the device by placing it in a known volume of water and measuring the displacement.
Remarkably, despite apparently being made of materials significantly denser than water, it floated.
We next tried to use a straightened paperclip to push it down into the water, and measured a volume of around 100 ml.
However, the temperature of the paperclip increased rapidly, apparently through contact with the artifact. 
Indeed, Luke's fingers were burned.
We observed that the temperature of the water had increased substantially --- by nearly twenty degrees Celsius in under a minute.
Further tests revealed the subject to be emitting broadly in the infrared.
Additionally, we found that the temperature increase was specific to the application of a downward force in water.
A downward force on a table produced no temperature change, nor did a sideways force in water.
The temperature change did not appear to be sensitive to where we pushed (on the gem or the setting).
Again, it seems obvious that a device which rapidly produces so much heat when pushed underwater could serve as a rather simple and straightforward source of electricity; however, it is unclear where the energy for the temperature increase originates, and we prescribe several more weeks of testing.

\subsection{Radioactivity}
Our observations consistently showed the subject to be unremarkable in terms of its alpha, beta, and gamma emissions.

\section{Conclusions}\label{conclusions}
The subject appears to possess some degree of situational awareness, based on its behavior in water and in the presence of a magnetometer.
The four hours of study we were permitted on the subject were insufficient for fully interrogating the range of possibilities produced by our testing, and the tests we performed have produced more questions than answers.

We urge extreme caution when transporting the subject due to its unpredictable behavior in a gravitational field.
It is unclear how the artifact would behave, for example, in orbit --- or on the way to orbit.
Similarly, the rapid temperature increase could pose a serious fire hazard, and we lacked sufficient time to determine if submersion in other materials would also produce rapid heating.

%\bibliographystyle{abbrv}
%\bibliography{main}

\end{document}
This is never printed